Linting Linearity in Core/System FC

### 2023-10-02 prototype/core-plugin-results.tex
First final version finished

\begin{figure}[h]
\centering{
\begin{tabular}{c|c|c|c|c|c}
    \thead{Library} & \thead{Total\\Accepted} & \thead{Total\\Rejected} & \thead{Unique\\Rejected} & \thead{Case-Var\\Rejected} & \thead{Unknown\\Rejected}\\
    linear-smc & 19438 & 4 & 1 & 1 & 0\\
    linear-base & 92308 & - & - & - & -\\
\end{tabular}
}
\caption{Linear Core Plugin on Linear Libraries}
\label{fig:core-plugin-res}
\end{figure}

>>>>

\begin{figure}[h]
\centering{
\begin{tabular}{c|c|c|c|c|c|c|c}
    \thead{Library} & \thead{Total\\Accepted} & \thead{Total\\Rejected} & \thead{Unique\\Rejected} & \thead{Linear modulo\\Call-by-name} & \thead{Linear\\Rejected} & \thead{$\lnot$ Linear\\Rejected} & \thead{Unknown\\Rejected}\\
    linear-smc & 19438 & 4 & 1 & 1 & 0 & 0 & 0\\
    linear-base & 91516 & 499 & 72 & 10 & 8 & 2 & 52\\
\end{tabular}
}
\caption{Linear Core Plugin on Linear Libraries}
\label{fig:core-plugin-res}
\end{figure}
